### 2018-09-03 Sections/optical_encoding_of_quantum_information.tex

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[width=0.15\textwidth]{photonic_qubit_encodings_long}
	\caption{Three approaches to encoding a single qubit using a single photon, via a superposition across two spatial ($A$ and $B$), polarisation ($V$ and $H$) or temporal ($t$ and \mbox{$t+\tau$}) modes.} \label{fig:photonic_qubit_encodings}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[width=0.5\textwidth]{photonic_qubit_encodings}
	\caption{Three approaches to encoding a single qubit using a single photon, via a superposition across two spatial ($A$ and $B$), polarisation ($V$ and $H$) or temporal ($t$ and \mbox{$t+\tau$}) modes.} \label{fig:photonic_qubit_encodings}
	\end{figure*}
\fi

@@

\begin{figure}[!htbp]
\includegraphics[width=0.3\textwidth]{pol_to_dual_conversion}
\caption{Conversion from single-photon polarisation encoding to dual-rail encoding, using a polarising beamsplitter (PBS) and wave-plate (WP). The PBS separates the polarisation components into two distinct spatial modes. The WP then rotates the polarisation of one of the spatial modes such that it has the same polarisation as the other. Conversion from dual-rail to polarisation encoding is just the reverse of this procedure.} \label{fig:pol_to_dual_conv}\index{Polarising beamsplitters}
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{hermite_basis}
	\caption{The family of Hermite functions, $H_n(x)$, modulated by Gaussian envelopes, are an example of an orthonormal basis of continuous functions that could be utilised in the spatio-temporal encoding of qudits into photonic wave-packets. Shown here are \mbox{$n=0,1,2,3$}.}\index{Hermite functions}\label{fig:hermite_basis}
\end{figure}

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{TEM_cylinder}\\
	\includegraphics[width=0.475\textwidth]{TEM_rectangular}
	\caption{TEM$_{m,n}$ modes for cylindrical (top) and rectangular (bottom) mode profiles.}\index{Transverse electro-magnetic (TEM) modes}\label{fig:TEM_modes}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[width=0.49\textwidth]{TEM_cylinder}
	\includegraphics[width=0.49\textwidth]{TEM_rectangular}
	\caption{TEM$_{m,n}$ modes for cylindrical (left) and rectangular (right) mode profiles.}\index{Transverse electro-magnetic (TEM) modes}\label{fig:TEM_modes}
	\end{figure*}
\fi

@@

\begin{figure}[!htbp]
\includegraphics[width=0.25\textwidth]{time_bin_encoding}
\caption{Time-bin encoding on an $n$-level quantum system. Time-bin are temporally localised with envelopes $\xi_j$, orthogonal to all others, different only via temporal displacements. The temporal separation between each consecutive time-bin is given by $\tau$.}\label{fig:time_bin_encoding}	
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.4\textwidth]{coherent_state_encoding}
\caption{Phase-space representation of a coherent state with complex amplitudes $\pm\alpha$. For sufficiently large amplitude one can approximate orthogonality, enabling a qubit encoding.} \label{fig:coherent_state_encoding}	
\end{figure}

>>>>

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[width=0.15\textwidth]{photonic_qubit_encodings_long}
	\captionspacefig \caption{Three approaches to encoding a single qubit using a single photon, via a superposition across two spatial ($A$ and $B$), polarisation ($V$ and $H$) or temporal ($t$ and \mbox{$t+\tau$}) modes.} \label{fig:photonic_qubit_encodings}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[width=0.5\textwidth]{photonic_qubit_encodings}
	\captionspacefig \caption{Three approaches to encoding a single qubit using a single photon, via a superposition across two spatial ($A$ and $B$), polarisation ($V$ and $H$) or temporal ($t$ and \mbox{$t+\tau$}) modes.} \label{fig:photonic_qubit_encodings}
	\end{figure*}
\fi

@@

\begin{figure}[!htbp]
\includegraphics[width=0.3\textwidth]{pol_to_dual_conversion}
\captionspacefig \caption{Conversion from single-photon polarisation encoding to dual-rail encoding, using a polarising beamsplitter (PBS) and wave-plate (WP). The PBS separates the polarisation components into two distinct spatial modes. The WP then rotates the polarisation of one of the spatial modes such that it has the same polarisation as the other. Conversion from dual-rail to polarisation encoding is just the reverse of this procedure.} \label{fig:pol_to_dual_conv}\index{Polarising beamsplitters}
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{hermite_basis}
	\captionspacefig \caption{The family of Hermite functions, $H_n(x)$, modulated by Gaussian envelopes, are an example of an orthonormal basis of continuous functions that could be utilised in the spatio-temporal encoding of qudits into photonic wave-packets. Shown here are \mbox{$n=0,1,2,3$}.}\index{Hermite functions}\label{fig:hermite_basis}
\end{figure}

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{TEM_cylinder}\\
	\includegraphics[width=0.475\textwidth]{TEM_rectangular}
	\captionspacefig \caption{TEM$_{m,n}$ modes for cylindrical (top) and rectangular (bottom) mode profiles.}\index{Transverse electro-magnetic (TEM) modes}\label{fig:TEM_modes}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[width=0.49\textwidth]{TEM_cylinder}
	\includegraphics[width=0.49\textwidth]{TEM_rectangular}
	\captionspacefig \caption{TEM$_{m,n}$ modes for cylindrical (left) and rectangular (right) mode profiles.}\index{Transverse electro-magnetic (TEM) modes}\label{fig:TEM_modes}
	\end{figure*}
\fi

@@

\begin{figure}[!htbp]
\includegraphics[width=0.25\textwidth]{time_bin_encoding}
\captionspacefig \caption{Time-bin encoding on an $n$-level quantum system. Time-bin are temporally localised with envelopes $\xi_j$, orthogonal to all others, different only via temporal displacements. The temporal separation between each consecutive time-bin is given by $\tau$.}\label{fig:time_bin_encoding}	
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.4\textwidth]{coherent_state_encoding}
\captionspacefig \caption{Phase-space representation of a coherent state with complex amplitudes $\pm\alpha$. For sufficiently large amplitude one can approximate orthogonality, enabling a qubit encoding.} \label{fig:coherent_state_encoding}	
\end{figure}

### 2018-09-03 Sections/optical_stability_in_quantum_networks.tex

\startnormtable
\begin{table}[!htbp]
	\begin{tabular}{|c|c|}
		\hline
  		\rowcolor{Dandelion} Protocol & Interference type \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Cluster state measurement & None \\
   		\rowcolor{LimeGreen} Quantum anonymous broadcasting & None \\
  		\rowcolor{LimeGreen} QKD (BB84, E91) & None \\
  		\rowcolor{LimeGreen} Quantum memory & None \\
  		\rowcolor{LimeGreen} Quantum process tomography & None \\
  		\rowcolor{LimeGreen} Quantum state tomography & None \\
  		\rowcolor{LimeGreen} Random number generation & None \\
  		\rowcolor{LimeGreen} Separable measurements & None \\
  		\rowcolor{LimeGreen} Separable state preparation & None \\
  		\rowcolor{LimeGreen} Optical interfacing & None \\
  		\hline
  		\rowcolor{Apricot} Cluster state preparation (fusion gates) & HOM \\
  		\rowcolor{Apricot} Entanglement purification & HOM \\
  		\rowcolor{Apricot} Entanglement swapping & HOM \\ 
  		\rowcolor{Apricot} Matter qubit entangling operations & HOM \\
  		\rowcolor{Apricot} Partial Bell state measurements & HOM \\
   		\rowcolor{Apricot} Quantum gate teleportation & HOM \\
  		\rowcolor{Apricot} Quantum state teleportation & HOM \\
  		\rowcolor{Apricot} Superdense coding & HOM \\
  		\hline
  		\rowcolor{Lavender} \textsc{BosonSampling} & MZ \\
  		\rowcolor{Lavender} General linear optics networks & MZ \\
  		\rowcolor{Lavender} Universal LOQC (KLM) & MZ \\
  		\rowcolor{Lavender} Quantum metrology & MZ \\
  		\rowcolor{Lavender} Quantum walks & MZ \\
    	\hline
	\end{tabular}
	\captionspacealg \caption{Summary of the major quantum network protocols presented in Sec.~\ref{sec:protocols_quant_int}, and their required type of interference.}\index{Interferometric requirements}\label{table:summary_inter}
\end{table}

>>>>

\startnormtable
\begin{table}[!htbp]
	\begin{tabular}{|c|c|}
		\hline
  		\rowcolor{Dandelion} Protocol & Interference type \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Cluster state measurement & None \\
   		\rowcolor{LimeGreen} Quantum anonymous broadcasting & None \\
  		\rowcolor{LimeGreen} QKD (BB84, E91) & None \\
  		\rowcolor{LimeGreen} Quantum memory & None \\
  		\rowcolor{LimeGreen} Quantum process tomography & None \\
  		\rowcolor{LimeGreen} Quantum state tomography & None \\
  		\rowcolor{LimeGreen} Random number generation & None \\
  		\rowcolor{LimeGreen} Separable measurements & None \\
  		\rowcolor{LimeGreen} Separable state preparation & None \\
  		\rowcolor{LimeGreen} Optical interfacing & None \\
  		\hline
  		\rowcolor{Apricot} Cluster state preparation (fusion gates) & HOM \\
  		\rowcolor{Apricot} Entanglement purification & HOM \\
  		\rowcolor{Apricot} Entanglement swapping & HOM \\ 
  		\rowcolor{Apricot} Matter qubit entangling operations & HOM \\
  		\rowcolor{Apricot} Partial Bell state measurements & HOM \\
   		\rowcolor{Apricot} Quantum gate teleportation & HOM \\
  		\rowcolor{Apricot} Quantum state teleportation & HOM \\
  		\rowcolor{Apricot} Superdense coding & HOM \\
  		\hline
  		\rowcolor{Lavender} \textsc{BosonSampling} & MZ \\
  		\rowcolor{Lavender} General linear optics networks & MZ \\
  		\rowcolor{Lavender} Universal LOQC (KLM) & MZ \\
  		\rowcolor{Lavender} Quantum metrology & MZ \\
  		\rowcolor{Lavender} Quantum walks & MZ \\
    	\hline
	\end{tabular}
	\captionspacetab \caption{Summary of the major quantum network protocols presented in Sec.~\ref{sec:protocols_quant_int}, and their required type of interference.}\index{Interferometric requirements}\label{table:summary_inter}
\end{table}

### 2018-09-03 Sections/optimising_the_world.tex

\begin{figure*}[!htbp]
	\includegraphics[width=0.6\textwidth]{traffic_optimisation}
	\captionspace \caption{A simple road network, where vertices represent intersections and edges represent roads. Edge weights indicate their associated travel time. The goal is for Alice and Bob to both drive home optimally, i.e minimising net commute time. Let us assume that the intersections do not delay single cars, but if they become congested (i.e more than one car simultaneously) they induce a time delay of 1 on all drivers present at the intersection. If Bob were to stay at work, and only Alice was attempting to drive home, her optimal route would be \mbox{$A\to D\to F$}, with a commute time of 2. Conversely, if Alice stayed at work and Bob was driving home, his optimal route would be \mbox{$B\to D\to G$}, also with a commute time of 2. However, if both Alice and Bob were driving home at the same time there would be congestion at intersection $D$, and their combined travel time would be 6, not the intended 4. Thus, by optimising their routes independently of one another their competition for intersection $D$ would penalise both of them by 1. On the other hand, a global optimisation would show that a more optimal routing would be for Alice to take \mbox{$A\to C\to F$} (time 2.5), with Bob remaining on \mbox{$B\to D\to G$} (time 2). This would penalise Alice by only 0.5 for taking the longer road, but both Alice and Bob would no longer be penalised at the congested intersection, reducing their collective transit time to 4.5, a saving of 1.5. Note that Alice and Bob are not only better off collectively (i.e their joint travel time), but also individually. That is, Alice making the sacrifice of taking the longer route home actually benefits her individually, with an individual saving of 0.5. In this trivial example there is only one point of conflict in the network. In general, as the number of users scales up, the distinct ways in which combinations of conflicts could emerge grows exponentially.}\label{fig:traffic_opt}
\end{figure*}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.3\textwidth]{3SAT}
\captionspace \caption{Digital circuit for an instance of the 3-\textsc{SAT} problem, with 4 clauses acting on input variables $\{x_i\}$. Each of the OR gates is input with some combination of 3 of the input bits or their compliments (i.e with a NOT gate). Each of these is referred to as a `clause', of which there are 4 in this example, but could be any number in general. The final AND gate requires that all clauses be simultaneously satisfied in order to yield a final output of `1'. The goal of the problem is to find an input bit-string $x$ that yields an output of `1'. In general, this may require exhaustively searching over the entire space of input states via brute-force, which exhibits time-complexity exponential in the length of the bit-string and associated number of clauses. This problem is proven to be \textbf{NP}-complete. Note that the similarly-defined 2-\textsc{SAT}\index{2-SAT problem} problem (i.e clauses each contain 2 input bits) is \textbf{P}, making 3-\textsc{SAT} the simplest model to consider in the study of \textbf{NP}-complete problems. For this reason 3-\textsc{SAT} is often used as the computational model when studying \textbf{NP}-complete problems.} \label{fig:3SAT}	
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.35\textwidth]{graph_colouring}\\
\includegraphics[width=0.35\textwidth]{four_colouring}
\captionspace \caption{(top) Example of a graph with 3-colouring, such that no two vertices connected by an edge share the same colour. For this particular graph, 3-colouring is optimal (in the sense that the number of colours in minimised). It can easily be seen upon inspection that no 2-colouring is possible for this graph. Thus, this graph's chromatic number is \mbox{$\chi(G)=3$}\index{Chromatic number}. (bottom) A 4-colouring of the states of France\index{Elderberries}. Any planar map such as this has a chromatic number of at most 4 -- the `four colour theorem'.}\index{Graph colouring}\index{Surrender}\label{fig:graph_colouring}	
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{search_tree}
	\captionspace \caption{A search tree\index{Search tree} is an outwardly-directed tree graph in which each vertex represents a state of the system (i.e `board position' in chess\index{Chess}). Edges represent actions (or `moves') available from the position from which the edge emanates. The root node represents the current position, and the depth of a vertex (i.e it's distance from the root node) represents its future time. A path through the tree therefore represents a sequence of moves up to some point in future time. If the tree had maximum depth, a route (from root to leaf) would represent an entire single game, and the complete set of routes would represent all possible ways in which the game can be played. A complete analysis of a complete search tree with maximum depth would therefore allow us to exhaustively analyse all possible ways in which a game could be played to completion, enabling optimal gameplay. However, since the number of vertices/edges in a tree graph grows exponentially with depth, the configuration search space in a game grows exponentially with how may moves into the future we wish to explore, thereby strongly limiting tree depth in practical implementations.}\label{fig:search_tree}
\end{figure}

>>>>

\begin{figure*}[!htbp]
	\includegraphics[width=0.6\textwidth]{traffic_optimisation}
	\captionspacefig \caption{A simple road network, where vertices represent intersections and edges represent roads. Edge weights indicate their associated travel time. The goal is for Alice and Bob to both drive home optimally, i.e minimising net commute time. Let us assume that the intersections do not delay single cars, but if they become congested (i.e more than one car simultaneously) they induce a time delay of 1 on all drivers present at the intersection. If Bob were to stay at work, and only Alice was attempting to drive home, her optimal route would be \mbox{$A\to D\to F$}, with a commute time of 2. Conversely, if Alice stayed at work and Bob was driving home, his optimal route would be \mbox{$B\to D\to G$}, also with a commute time of 2. However, if both Alice and Bob were driving home at the same time there would be congestion at intersection $D$, and their combined travel time would be 6, not the intended 4. Thus, by optimising their routes independently of one another their competition for intersection $D$ would penalise both of them by 1. On the other hand, a global optimisation would show that a more optimal routing would be for Alice to take \mbox{$A\to C\to F$} (time 2.5), with Bob remaining on \mbox{$B\to D\to G$} (time 2). This would penalise Alice by only 0.5 for taking the longer road, but both Alice and Bob would no longer be penalised at the congested intersection, reducing their collective transit time to 4.5, a saving of 1.5. Note that Alice and Bob are not only better off collectively (i.e their joint travel time), but also individually. That is, Alice making the sacrifice of taking the longer route home actually benefits her individually, with an individual saving of 0.5. In this trivial example there is only one point of conflict in the network. In general, as the number of users scales up, the distinct ways in which combinations of conflicts could emerge grows exponentially.}\label{fig:traffic_opt}
\end{figure*}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.3\textwidth]{3SAT}
\captionspacefig \caption{Digital circuit for an instance of the 3-\textsc{SAT} problem, with 4 clauses acting on input variables $\{x_i\}$. Each of the OR gates is input with some combination of 3 of the input bits or their compliments (i.e with a NOT gate). Each of these is referred to as a `clause', of which there are 4 in this example, but could be any number in general. The final AND gate requires that all clauses be simultaneously satisfied in order to yield a final output of `1'. The goal of the problem is to find an input bit-string $x$ that yields an output of `1'. In general, this may require exhaustively searching over the entire space of input states via brute-force, which exhibits time-complexity exponential in the length of the bit-string and associated number of clauses. This problem is proven to be \textbf{NP}-complete. Note that the similarly-defined 2-\textsc{SAT}\index{2-SAT problem} problem (i.e clauses each contain 2 input bits) is \textbf{P}, making 3-\textsc{SAT} the simplest model to consider in the study of \textbf{NP}-complete problems. For this reason 3-\textsc{SAT} is often used as the computational model when studying \textbf{NP}-complete problems.} \label{fig:3SAT}	
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.35\textwidth]{graph_colouring}\\
\includegraphics[width=0.35\textwidth]{four_colouring}
\captionspacefig \caption{(top) Example of a graph with 3-colouring, such that no two vertices connected by an edge share the same colour. For this particular graph, 3-colouring is optimal (in the sense that the number of colours in minimised). It can easily be seen upon inspection that no 2-colouring is possible for this graph. Thus, this graph's chromatic number is \mbox{$\chi(G)=3$}\index{Chromatic number}. (bottom) A 4-colouring of the states of France\index{Elderberries}. Any planar map such as this has a chromatic number of at most 4 -- the `four colour theorem'.}\index{Graph colouring}\index{Surrender}\label{fig:graph_colouring}	
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{search_tree}
	\captionspacefig \caption{A search tree\index{Search tree} is an outwardly-directed tree graph in which each vertex represents a state of the system (i.e `board position' in chess\index{Chess}). Edges represent actions (or `moves') available from the position from which the edge emanates. The root node represents the current position, and the depth of a vertex (i.e it's distance from the root node) represents its future time. A path through the tree therefore represents a sequence of moves up to some point in future time. If the tree had maximum depth, a route (from root to leaf) would represent an entire single game, and the complete set of routes would represent all possible ways in which the game can be played. A complete analysis of a complete search tree with maximum depth would therefore allow us to exhaustively analyse all possible ways in which a game could be played to completion, enabling optimal gameplay. However, since the number of vertices/edges in a tree graph grows exponentially with depth, the configuration search space in a game grows exponentially with how may moves into the future we wish to explore, thereby strongly limiting tree depth in practical implementations.}\label{fig:search_tree}
\end{figure}

### 2018-09-03 Sections/protocols_for_the_quantum_internet.tex

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{telescope_array}
	\captionspacefig \caption{An array of quantum-enabled telescopes, paired with one another via Bell-pairs, distributed over a quantum network.}\label{fig:telescope_array}\index{Telescope arrays}
\end{figure}

>>>>

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{telescope_array}
	\captionspacefig \caption{An array of quantum-enabled telescopes, paired with one another via Bell-pairs, distributed over a quantum network. With more telescopes in the array, signal strength can be increased, and if the array has a 2D grid topology, rather than a linear one, the angles of incident light fields can be measured along multiple axes.}\label{fig:telescope_array}\index{Telescope arrays}
\end{figure}
